Papers

### 2024-11-15 quarto/index.qmd
update

* Join our Llama team for a 2025 research internship! Just email me if you are interested. <a href="https://x.com/astonzhangAZ/status/1843327816055795745" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available. <a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model. Check out <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">my developer podcast</a>. <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

@@

>>>>

* [<span style="color:red;">Hiring</span>] Join our Llama team for a 2025 research internship! Just email me if you are interested. <a href="https://x.com/astonzhangAZ/status/1843327816055795745" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* <a href="https://ai.meta.com/blog/meta-llama-3-1/" target="_blank">Llama 3.1 405B</a> is now openly available. <a href="https://x.com/astonzhangAZ/status/1815763885380747422" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>
* Meet <a href="https://ai.meta.com/blog/meta-llama-3/" target="_blank">Llama 3</a>, our state-of-the-art open source large language model. Check out <a href="https://x.com/AIatMeta/status/1806757387677897206" target="_blank">my developer podcast</a>. <a href="https://x.com/astonzhangAZ/status/1780990210576441844" title="Tweet" target="_blank"><img src="./img/logo-twitter.svg" class="paper-icon"></a>

@@

* J. Ji, **A. Zhang**, C. Zhu, S. Wang, M. Kambadur, S. Chang, and W. Xiong<br>
<a href="#">Pruning Computations in Transformer Prefilling for Large Language Models</a><br>
*"Speed up Transfomer prefilling for generation via a learnable router."*
In *arXiv*, 2024<br>
